
% \begin{figure*}[t]
%                 \begin{lstlisting}[
%         %basicstyle = \ttfamily,
%         basicstyle = \small,
%         columns = fixed,
%         tabsize=8,
%         %frame = l,
%         xleftmargin=.18\textwidth,
%         language = C
%         ]
        
% #define __va(x) ((void *)((unsigned long)(x) + PAGE_OFFSET))
% #define __pa(x) ((unsigned long)(x) - PAGE_OFFSET)

% #define virt_to_pfn(kaddr)      (__pa(kaddr) >> PAGE_SHIFT)
% #define pfn_to_virt(pfn)        __va((pfn) << PAGE_SHIFT)

% /* memmap is virtually contiguous.  */
% #define __pfn_to_page(pfn)      (vmemmap + (pfn))  
% #define __page_to_pfn(page)     (unsigned long)((page) - vmemmap)
%                 \end{lstlisting}
%         \caption{ Linux kernel macros for translation between KVA, PFN and \page{}.
%                 }
%       \label{fig:mem_model}
% \end{figure*}

\subsection{OS Defences}

Other than DMA attacks, OS developers have to worry about code injection originating from unprivileged users, such as buffer overflow attacks \cite{nx, kalsr}.
We discuss the common mechanisms used to mitigate such attacks in the kernel. Subverting these countermeasures is essential to execute a successful DMA attack.

\paragraph{NX-BIT}\label{sec:nx-bit}

A malicious device can inadvertently gain write access to a function pointer and consequently gain the ability to inject malicious code. 
To protect against such threats, modern OSs make use of hardware support, namely the No-eXecute bit, to prevent code execution from data pages. This bit is defined for each page in MMU’s page tables. Whenever the CPU tries to fetch code from memory, this bit is validated. When set, the CPU raises an exception to the OS instead of executing the code. The NX-bit method is also known as the W $\oplus$ X (Write $\oplus$ eXecute) or DEP (Data Execution Prevention). 
A DMA capable device rarely has access to kernel text regions. Thus the NX-bit is effective in preventing simple code injection attacks.

Return Oriented Programming (ROP) is a common method used by malware to bypass DEP (i.e., NX-bit) defenses \cite{RBSS12}. ROP exploits the fact that the CPU stack pointer may point to any data page. To set up an attack from a data page, the attacker builds a poisoned stack filled with required data and pointers to specific locations in the code section (a.k.a., ROP gadgets). Each gadget is a short piece of code (usually one or two instructions) and a return instruction. When the CPU executes a return instruction, the return address and thus the address of the next instruction to execute is taken from the stack. In the poisoned stack, each return address points to the next gadget and so on. 
 
By carefully selecting these gadgets, an attacker can execute any payload. To bootstrap a ROP attack, an attacker must modify the stack pointer register to the address of the poisoned stack. This is often achieved with another DEP circumventing technique, i.e., Jump Oriented Programming (JOP) \cite{BJFL11}. JOP uses, \texttt{jump} instructions instead of \texttt{return} instructions and, thus, does not require a poisoned stack.

\paragraph{KASLR}\label{sec:kaslr}

To successfully execute a code injection attack, the attacker must know the memory layout. Specifically, the address of the code section is required for finding ROP gadgets (Sec. \ref{sec:nx-bit}). 

Address Space Layout Randomization (ASLR) is a common mechanism for mitigating code injection attacks in the context of user-level processes. Systems that support ASLR randomize the memory layout for each process on every execution. This way, ROP attacks built for a specific layout, fail. Similarly, KASLR \cite{kalsr} randomizes the kernel memory layout.

The Linux kernel has a predetermined virtual memory layout \cite{mem_layout}. This layout defines the location of the kernel text mapping, the direct mapping of physical memory and the virtual memory. KASLR randomizes their offsets each reboot.

Since KASLR randomizing only the base address of the kernel text mapping, text addresses always appear in the following range \texttt{[0xffffffff80000000,0xffffffffa0000000)} (Fig. \ref{fig:mem_layot}) and, therefore are easy to detect. KASLR kernel text is aligned to 2~MB borders. This is the result of page table restrictions and unlikely to change, which means that the lowest 21 bits remain unchanged. Hence, knowing even a single address of a known element is sufficient to deduce the base address and compromise KASLR. Once the base address is known, the attacker can use it to create a ROP stack.
%\adam{from here -->}
To identify this first pointer, malicious devices can scan pages mapped for reading looking for kernel pointers, leaked due to \subpage{} vulnerability. Once such a pointer is identified, all that remains is to reduce the offset of the symbol in the binary from the pointer to get the base address.

In fact, during our investigation, we have found that there is a symbol visible to both FireWire and NICs in Linux 5.0, making it suitable for compromising KASLR. Specifically, as of version 2.6.24, Linux supports network namespaces and every network object, and in particular, sockets have a pointer to their namespace object. One such object, namely a global namespace object, \texttt{init\_net}, is always defined. By scanning leaked pages during I/O and utilizing the fact that the lower 21 bits of the text region, as aforementioned, are never modified, we can identify \texttt{init\_net} with high probability.
%\adam{<-- and up to here, it's not really background.  At the very least, put it in its own subsection ``how DMA attacks can break KASLR'' or you risk reviewers missing this point, since people are familiar with ASLR and might skip the relevant background section}

The direct mapping base (\texttt{page\_offset\_base}) and virtual memory map (\texttt{vmemmap\_base}) are also randomized (Fig. \ref{fig:mem_layot}), where each regions base pointer is randomized respecting a 1~GB alignment. This means that the lower 30 bits are unmodified and can leak both the PFN numbers and the randomized offset. This alignment is also due to page table considerations. That is, the page upper table (PUD) has a 30~bit shift. Once the random offsets \textit{PAGE\_OFFSET} and \textit{vmemmap} for direct mapping base and virtual memory map are known it becomes possible to translate between a \kva{} (kernel virtual addresses within the direct mapping region) its PFN and, its \page{} address (virtual memory map region).
%The translation macros are shown in Fig. \ref{fig:mem_model}. 

\subsection{\textcolor{red}{Adaptation of OS defences}}

\begin{table*}[t]
\begin{adjustbox}{max width=0.9\textwidth}
\begin{tabular}{l||cccccc}
OS                           & IOMMU         & default mode & IOVA map   & memory    & KASLR & DMA attacks          \\ \hline\hline
Windows 10 \textless 1803    & Not supported & N/A          & N/A        & shared    & Yes   & demonstrated         \\
Windows 10 \textgreater 1803 & supported     & On       & per device & dedicated & Yes   & unknown*                 \\
MacOS \textless 10.12.4      & supported     & On       & shared     & dedicated & Yes   & demonstrated             \\
MacOS \textgreater 10.12.4   & supported     & On       & shared     & dedicated & Yes   & unknown*                 \\
FreeBSD                      & supported     & Off           & per device & dedicated & Yes   & demonstrated        \\
MINIX 3                      & supported     & On       & ?          & dedicated & No    & unknown                  \\\hline
Linux                        & supported     & On     & per device & shared    & Yes   & \textbf{\begin{tabular}[c]{@{}c@{}}demonstrated in this paper \\ (previously unknown)\end{tabular}} \\\hline\hline           
\end{tabular}
\end{adjustbox}
  \caption{IOMMU adaptation in different OS's (* stands for previously known but yet untested, in the new version, vulnerabilities.}
  \label{tab:other_os}
\end{table*}

The current state of IOMMU adaptation varies among different OS vendors. We briefly discuss other OSes and summarize the data in Table~\ref{tab:other_os}. 

\smallskip
\noindent\textbf{Windows.} Until recently (2019) Windows had no IOMMU support exposing it to simple DMA attacks\cite{thunder}.
In 2019 (with build 1803) Microsoft has introduced Kernel DMA Protection\cite{ms_iommu}, which provides IOMMU protection by default with dedicated I/O page table per device. 
In addition network buffers are allocated from dedicated pools of memory, which limits the possible exposure of sensitive data. But a brief exploration of the Windows Networking drivers API, reveals functions like \emph{NdisAllocateNetBufferMdlAndData}\cite{ms_single} that allocates a NET\_BUFFER structure and data in a single memory buffer, exposing the OS to \simple attacks. Note that the NET\_BUFFER vulnerability was previously described\cite{thunder}. 

\smallskip
\noindent\textbf{MacOS.} IOMMU is enabled by default. It also uses dedicated memory for network I/O. MacOS however does expose the \textit{mbuf} data structure to the device, though with some precautions such as blinding an exposed callback pointer by XORing with a secret cookie. While stopping \simple attacks, such an exposure of metadata opens up the MacOS to potential \compound attacks. 

\smallskip
\noindent\textbf{FreeBSD.} An \textit{mbuf} struct through which the \textit{ext\_free} callback is exposed as demonstrated by Merketos\cite{thunder}. To the best of our knowledge (October 2020), this vulnerability still exists in the FreeBSD kernel. 

\smallskip
\noindent\textbf{Minix.} An honorable mention goes to the Minix micro-kernel\cite{minix} which is present on Intel chipsets. It has been shown to have a DMA vulnerability at initialization time\cite{minix_intc}. The MINIX micro-kernel pre-allocates memory for I/O and copies in/out any sent/received data bytes, effectively stopping known DMA attacks. 

\section{Threat Model}\label{sec:threat_model}

Our attacks are designed with the following assumptions:
\begin{enumerate}
    \item We assume the existence of a malicious DMA capable device attached to the system.
    \item The actual attack is performed solely by a DMA-capable malicious device.
    \item Any hardware aside from the specific malicious device is working as expected.
 \end{enumerate}

The most significant potential consequence of our attacks is privilege escalation, which allows attackers to execute arbitrary code with kernel privileges. Another potential consequence we consider is a full system memory dump. These are harder to thwart and even harder to detect. Lastly, a consequence of a possible failed attack is random memory corruption, resulting in a denial of service \cite{MMT16}, where the OS panics. Ideally, malformed devices should not be able to crash the entire system. 
